%% ------------------------------ Abstract ---------------------------------- %%
\begin{abstract}

In this data explosion era, there are myriad programs that are executed repeatedly on large sets of data, consuming high amounts of energy and resources. Critical process reused on different data sets will no doubt help reduce the time and computations.

This thesis explores how Computation Reuse can be implemented for augmenting the performance of some time consuming data analytics algorithms. Specifically, we developed a general framework for efficiently finding similar datasets and effectively reusing history. We demonstrated the large benefits (up to 20X in average case and upto 200X in best case) on K-means and SGD-based SVM algorithm. 




\end{abstract}


%% ---------------------------- Copyright page ------------------------------ %%
%% Comment the next line if you don't want the copyright page included.
\makecopyrightpage

%% -------------------------------- Title page ------------------------------ %%
\maketitlepage

%% -------------------------------- Dedication ------------------------------ %%
\begin{dedication}
 \centering To my parents and specially to my maternal grandmother for her unwavering support and the constant belief that I would be successful in my ventures.
\end{dedication}

%% -------------------------------- Biography ------------------------------- %%
\begin{biography}
The author was born in the small town Sitapur in India. He attended Guru Gobind Singh Indraprastha University, Delhi where he obtanined his  Bachelor’s in Information Technology from Maharaja Surajmal Institute of Technology. After graduation he worked for a couple of years in a startup, being one of the first members of the tech team and helped build it into a global barnd in the field of AB testing. He was admitted to NC State in the Fall of 2013 as a Master’s student to the Department of Computer Science. He has worked under Dr. Xipeng Shen as a Research Assistant since August 2015 with research in the area of Algorithmic Optimization, which has culminated with this a new methodology for the Initialization of converging algorithms with History Reuse, which has been documented in this thesis.
\end{biography}

%% ----------------------------- Acknowledgements --------------------------- %%
\begin{acknowledgements}

I would like to express my gratitude to my advisor Dr Xipeng Shen  for the useful comments, remarks and engagement through the learning process of this master thesis. His constant guidance through the process has been invaluable, be it teaching me the correct research methodology or discussing with me solutions for problems. His constant guidance was imperative in the successful completion of this thesis.

I would also like to take this opportunity to thank Dr Frank Meuller for providing me help with all the hardware that I needed for experimentation and agreeing to serve on my thesis committee. 

I would also like to thank Dr. Min Chi for serving on my thesis committee.

Last but not the least, I would like to thank my loved ones, who have supported me throughout entire process, both by keeping me harmonious and helping me putting pieces together. I will be grateful forever for your love.

\end{acknowledgements}


\thesistableofcontents

\thesislistoftables

\thesislistoffigures